Investigating the influence of genre preferences on movie/series rating patterns

### 2024-03-24 gen/paper/paper.Rmd

| Name of Variable | Contents of Variable                                                                                                                                             | Used as .. in Analysis |
|------------|-------------------------------------------------|------------|
| Average Rating   | The average rating on IMBd per title of a given movie or series.                                                                                                 | Dependent Variable     |
| Genre Types      | Genre Types is a cluster for all 26 genre dummies that contain the value 1 if the movie or series contains that genre and otherwise 0.                           | Independent Variable   |
| titleType        | This variable indicates whether a title is a movie or a series.                                                                                                  | Fixed Effect           |
| Title            | The title is the given title of any unique movie or series                                                                                                       | Fixed Effect           |
| 5 Year Window    | The 5 year windown (or ' slide_window_5' indicates between what 5 year window a movie or series belongs to. For example a movie from 2003 belonging to 2000-2004 | Split Varible          |

>>>>

| Name of Variable | Contents of Variable                                                                                                                                             | Used as .. in Analysis |
|------------|-------------------------------------------------|------------|
| Average Rating   | The average rating on IMBd per title of a given movie or series.                                                                                                 | Dependent Variable     |
| Genre Types      | Genre Types is a cluster for all 26 genre dummies that contain the value 1 if the movie or series contains that genre and otherwise 0.                           | Independent Variable   |
| titleType        | This variable indicates whether a title is a movie or a series.                                                                                                  | Fixed Effect           |
| Title            | The title is the given title of any unique movie or series                                                                                                       | Fixed Effect           |
| 5 Year Window    | The 5 year window (or ' slide_window_5' indicates between what 5 year window a movie or series belongs to. For example a movie from 2003 belonging to 2000-2004 | Split Variable          |

### Descriptives
The data set contains of 70087 films, of which 60246 are movies and 9841 are series.  These films have on average a rating of 6.3, with 10 being the highest and 1 being the lowest. After removing the votes to all being above 100, the average number of votes on a film became 7146. When looking at the years, the most amount of films were released on IMDb in 2019, with 2586 films. Also when comparing the 5 year range of films released,2015 to 2019 had the most films released, with 11353 films. Looking at the runtime of the films, on average a film is 101 minutes long.
